### 2014-02-13 paper/manuscript.tex
Made paper buildable without figures
- also added corresponding author information
- minor README formatting changes

@@

\graphicspath{{../figures/}}
%% \newcommand{\hidefigures}{\relax}

@@

\ \\
{\bf \large Eric Hunsberger$^{\displaystyle 1}$, Matthew Scott$^{\displaystyle 2}$, Chris Eliasmith$^{\displaystyle 1}$}\\
{$^{\displaystyle 1}$Centre for Theoretical Neuroscience, University of Waterloo, Waterloo, Canada.}\\
{$^{\displaystyle 2}$Department of Applied Mathematics, University of Waterloo, Waterloo, Canada.}\\
%

>>>>

%%%%% options, to be defined externally
%% \newcommand{\hidefigures}{\relax}

@@

\graphicspath{{../figures/}}

@@

\ \\
{\bf \large Eric Hunsberger$^{1*}$, Matthew Scott$^2$, Chris Eliasmith$^1$}\\
{$^1$Centre for Theoretical Neuroscience, University of Waterloo, Waterloo, Canada.}\\
{$^2$Department of Applied Mathematics, University of Waterloo, Waterloo, Canada.}\\
{$^*$Corresponding author: ehunsber@uwaterloo.ca}\\
%
